The Driving Forces of API Evolution

### 2015-06-04 thesis/paper.tex
widows+orphans
Fixed broken reference

\subsubsection{APIs as Systems}
Company A's API is rather complex, and in addition to the API interface and implementation code, it includes a middle-layer which manages error handling and the access to various 3\textsuperscript{rd} party libraries. In this study, we use the API interface and the middle-layers as units of analysis. Examples of where the responsibilities exceed those of a primitive API interface is that it includes functionality such as error handling and a daemon which facilitates communication between hardware entities. In addition to that is an SDK which includes the API documentation, user manuals and example applications that utilise the API code. Based on these characteristics and the IEEE definition of a system, which reads as follows; ``A combination of interacting elements organised to achieve one or more stated purposes...Organised to accomplish a specific function or set of functions within a specific environment" \cite{5733835 }, we consider the API to be a system because of the combination of the interacting parts of the API, coupled with the specific nature of the problem the API is addressing.

>>>>

\subsubsection{APIs as Systems}
Company A's API is rather complex, and in addition to the API interface and implementation code, it includes a middle-layer which manages error handling and the access to various 3\textsuperscript{rd} party libraries. In this study, we use the API interface and the middle-layers as units of analysis. Examples of where the responsibilities exceed those of a primitive API interface is that it includes functionality such as error handling and a daemon which facilitates communication between hardware entities. In addition to that is an SDK which includes the API documentation, user manuals and example applications that utilise the API code. Based on these characteristics and the IEEE definition of a system, which reads as follows; ``A combination of interacting elements organised to achieve one or more stated purposes...Organised to accomplish a specific function or set of functions within a specific environment" \cite{5733835}, we consider the API to be a system because of the combination of the interacting parts of the API, coupled with the specific nature of the problem the API is addressing.
